Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-30 interviews.tex
move notebook stats to interview section
minor edits

Working in a shared environment also entails compromises about what you can
install. Byers says that installing random packages is part of exploratory data
analysis.

@@

Much of the time, commands typed at the R command line just serve a transitory
purpose, so having RCloud save commands into cells bothers experienced
users. Kenny notes, ``It saves everything I do like everything is gold, but most
of it is junk not meant to be saved.'' Rick says ``I just want to type in a
couple of quick and get some results that are going to tell me what to do next,
and they're not necessarily archival in any sense''

@@

Users also felt that cells do not capture the right level of granularity: they
either hold too much code or too little. Rick says that RCloud's cells structure
``tempts me to type a big long thing and then run the whole thing, as opposed to
typing a few little pieces that I'm thinking of on the inner parts and then put
them together to make the big thing'' as he would do on the command line. When
Taylor uses the R command line, he copies and pastes ``like 5-10 lines of code,
so when something breaks, I get an error message on that one line, and I can
up-arrow and change it and fix it, whereas in RCloud I have to run a whole cell,
so the only way to get that same functionality is if every line's in one
cell. Because if it runs lines 1, 2, 3, then 4 fails, I have to either run the
whole cell again, or have line 4 in its own cell. I can't rerun just one line.''

Cells can also take up substantial vertical space, requiring scrolling. Rick
complains that ``every time I type more stuff, the notebook gets longer and
longer and it's harder to deal with.'' Ivan says that cells' controls and blank
space take extra real estate compared to a straight command line, and he and
KCKC both complained that when there are long results or plots, it causes the
code to scroll off the screen. Raif: ``for example imagine I run a cell whose
output is huge, and now that output would block the whole window, and in order
to find the next cell, I have to scroll down, and find where that cell starts,
right? So, I'm losing the continuity of my code to the output''

Some users think users should have the option to keep results separate from the
code.  Ivan thinks that RStudio's layout is more helpful because the charts
are kept in another pane and stay in one place while doing analysis. Raif says
``cells are really useful'' but ``you want to see your output in a different
window [or] on a separate part of the window''.

The cell structure also can be problematic if some cells take a long time to
run. In Kenny's work, there is often a ``long tail''.  The first cell may take
seconds to run, the next cell minutes, and the last cell 5 hours.  In this
situation, the run whole notebook button is ``dangerous''. When converting
his work to notebooks, Kenny ends up with a lot of comments that say ``this cell
takes a long time to run.''

@@

\subsection{A sea of notebooks}
RCloud is starting to be a victim of its own success, as there are now too many
notebooks.  Rick doesn't find the notebook tree very useful for this reason: ``I
don't necessarily need to see everybody's notebook that uses RCloud'' ``every
time I do something new, I get a new notebook and so now my notebooks are maybe
50 or 60. That's enough to think about just on my own, but if I've got
everybody's 50 or 60 sitting on my display, I find that it's more than I want to
know about.''

>>>>

Working in a shared environment also entails compromises about what you can
install. Byers says installing alternative or nonstandard packages is
intrinsic to exploratory data analysis.

@@

Much of the time, commands typed at the R command line just serve a transitory
purpose, so having RCloud save commands into cells bothers experienced
users. Kenny notes, ``It saves everything I do like everything is gold, but most
of it is junk not meant to be saved.'' Rick says ``I just want to type in a
couple of quick commands and get some results that are going to tell
me what to do next, and they're not necessarily archival in any sense.''

@@

Users also felt that cells do not capture the right level of granularity: they
either hold too much code or too little. Rick says that RCloud's cell structure
``tempts me to type a big long thing and then run the whole thing, as opposed to
typing a few little pieces that I'm thinking of on the inner parts and then put
them together to make the big thing'' as he would do on the command line. When
Taylor uses the R command line, he copies and pastes ``like 5-10 lines of code,
so when something breaks, I get an error message on that one line, and I can
up-arrow and change it and fix it, whereas in RCloud I have to run a whole cell,
so the only way to get that same functionality is if every line's in one
cell. Because if it runs lines 1, 2, 3, then 4 fails, I have to either run the
whole cell again, or have line 4 in its own cell. I can't rerun just one line.''

Cells can also take up substantial vertical space, requiring scrolling. Rick
complains that ``every time I type more stuff, the notebook gets longer and
longer and it's harder to deal with.'' Ivan says that cells' controls and blank
space take extra real estate compared to a straight command line, and he and
KCKC both complained that when there are long results or plots, it causes the
code to scroll off the screen. Raif: ``for example imagine I run a cell whose
output is huge, and now that output would block the whole window, and to
find the next cell, I have to scroll down, and find where that cell starts,
right? So, I'm losing the continuity of my code.''

Some users would like the option to keep results separate from code. 
Ivan thinks that RStudio's layout is more helpful because charts
are kept in another pane and stay in one place while doing analysis. Raif says
``cells are really useful'' but ``you want to see your output in a different
window [or] on a separate part of the window''.

The cell structure also can be problematic if some cells take a long time to
run. In Kenny's work, there is often a ``long tail''.  The first cell may take
seconds to run, the next cell minutes, and the last cell 5 hours.  In this
situation, the Run Whole Notebook button is ``dangerous''. When converting
his work to notebooks, Kenny ends up with a lot of comments that say ``this cell
takes a long time to run.''

@@

\subsection{A sea of notebooks}
RCloud is starting to be a victim of its own success, as there are now too many
notebooks.  There are over 5000 notebooks on the research instance, of which
more than 500 have been starred and more than 350 have been forked.

Rick doesn't find the notebook tree very useful for this reason: ``I
don't necessarily need to see everybody's notebook that uses RCloud'' ``every
time I do something new, I get a new notebook and so now my notebooks are maybe
50 or 60. That's enough to think about just on my own, but if I've got
everybody's 50 or 60 sitting on my display, I find that it's more than I want to
know about.''
